Reasoning About a Machine with Local Capabilities

### 2018-05-09 toplas/paper.tex
Updated the illustration figure.
Removed individual captions and added a short
caption for all of the figure.

      % Stack pointer
      \begin{scope}
        \clip (4.6,5) rectangle (7.6,11.5);
        \capbrace[sp]{(4.6,5)}{(4.6,13)}
      \end{scope}
      \draw node[right=0cm of sp] { sp };
  \end{tikzpicture}
  \caption{We have been called by an adversary and are ready to return to the
    adversary.}
  \label{fig:illu-intro}
  \end{subfigure}
  \begin{subfigure}{0.333\linewidth}
    \begin{tikzpicture}[scale=.5, every node={scale=.5}]
    % recurrent parts
    \stdstackstart

@@

      % Stack pointer
      \begin{scope}
        \clip (4.6,2) rectangle (7.6,11.5);
        \capbrace[sp]{(4.6,2)}{(4.6,13)}
      \end{scope}
      \draw node[right=0cm of sp] { sp };
  \end{tikzpicture}
  \caption{If we do not clear our stack when we return to an adversary, then
    they can access our private data and capabilities. This could include old
    stack and program pointers.}
  \label{fig:illu-priv-data}
  \end{subfigure}
  \begin{subfigure}{0.333\linewidth}
    \begin{tikzpicture}[scale=.5, every node={scale=.5}]
    % recurrent parts
    \stdstackstart

@@

      % Stack pointer
      \begin{scope}
        \clip (4.6,2) rectangle (7.6,11.5);
        \capbrace[sp]{(4.6,2)}{(4.6,13)}
      \end{scope}
      \draw node[right=0cm of sp] { sp };
  \end{tikzpicture}
  \caption{Here we made sure to clear the stack before returning to the
    adversary. The adversary no longer has access to our private data and capabilities.}
  \label{fig:illu-clear-priv}
  \end{subfigure}

@@

      % Stack pointer
      \begin{scope}
        \clip (4.6,5) rectangle (7.6,11.5);
        \capbrace[sp]{(4.6,5)}{(4.6,13)}
      \end{scope}
      \draw node[right=0cm of sp] { sp };
  \end{tikzpicture}
  \caption{In this case, we have called an adversary as part of our program.}
  \label{fig:illu-call-adv}
  \end{subfigure}
  \begin{subfigure}{0.333\linewidth}
    \begin{tikzpicture}[scale=.5, every node={scale=.5}]
    % recurrent parts
    \stdstackstart

@@

      % Stack pointer
      \begin{scope}
        \clip (4.6,2) rectangle (7.6,11.5);
        \capbrace[sp]{(4.6,2)}{(4.6,13)}
      \end{scope}
      \draw node[right=0cm of sp] { sp };
  \end{tikzpicture}
  \caption{If we return to the adversary after the situation in
    \figurename~\ref{fig:illu-call-adv}, the adversary has access to the
    contents of the stack from the call to the adversary. This could include the
    return pointer, we gave to the adversary.}
  \label{fig:illu-adv-data}
  \end{subfigure}
  \begin{subfigure}{0.333\linewidth}
    \begin{tikzpicture}[scale=.5, every node={scale=.5}]
    % recurrent parts
    \stdstackstart

@@

      % Stack pointer
      \begin{scope}
        \clip (4.6,2) rectangle (7.6,11.5);
        \capbrace[sp]{(4.6,2)}{(4.6,13)}
      \end{scope}
      \draw node[right=0cm of sp] { sp };
  \end{tikzpicture}
  \caption{Here we made sure to clear all of the stack, including the part we
    gave the adversary access to.}
  \label{fig:illu-clear-all}
  \end{subfigure}

  \caption{In this section, we illustrate the stack in different scenarios
    related to returning to an adversary. }
  \label{fig:ret-adv}
\end{figure}
\textbf{Invoking the adversary} A slightly more complex case is invoking the
adversary. As above, we clear all the non-argument registers, as well as the
part of the stack that we are not using (because, as above, it may contain local
capabilities from previously executed code that the adversary could exploit in
the same way). We leave a copy of the stack pointer in $r_\stk$, but only after
we have used the $\subseg{}{}{}$ instruction to shrink its authority to the part
that we are not using ourselves.

>>>>

      % Stack pointer
      \begin{scope}
        \clip (4.6,5) rectangle (7.6,11.5);
        \capbrace[sp]{(4.6,5)}{(4.6,12)}
      \end{scope}
      \draw node[right=0cm of sp] { sp };
    \end{tikzpicture}
    \caption{}
  \label{fig:illu-intro}
  \end{subfigure}
  \begin{subfigure}{0.333\linewidth}
    \begin{tikzpicture}[scale=.5, every node={scale=.5}]
    % recurrent parts
    \stdstackstart

@@

      % Stack pointer
      \begin{scope}
        \clip (4.6,2) rectangle (7.6,11.5);
        \capbrace[sp]{(4.6,2)}{(4.6,12)}
      \end{scope}
      \draw node[right=0cm of sp] { sp };
    \end{tikzpicture}
  \caption{}
  \label{fig:illu-priv-data}
  \end{subfigure}
  \begin{subfigure}{0.333\linewidth}
    \begin{tikzpicture}[scale=.5, every node={scale=.5}]
    % recurrent parts
    \stdstackstart

@@

      % Stack pointer
      \begin{scope}
        \clip (4.6,2) rectangle (7.6,11.5);
        \capbrace[sp]{(4.6,2)}{(4.6,12)}
      \end{scope}
      \draw node[right=0cm of sp] { sp };
    \end{tikzpicture}
  \caption{}
  \label{fig:illu-clear-priv}
  \end{subfigure}

@@

      % Stack pointer
      \begin{scope}
        \clip (4.6,5) rectangle (7.6,11.5);
        \capbrace[sp]{(4.6,5)}{(4.6,13)}
      \end{scope}
      \draw node[right=0cm of sp] { sp };
    \end{tikzpicture}
  \caption{}
  \label{fig:illu-call-adv}
  \end{subfigure}
  \begin{subfigure}{0.333\linewidth}
    \begin{tikzpicture}[scale=.5, every node={scale=.5}]
    % recurrent parts
    \stdstackstart

@@

      % Stack pointer
      \begin{scope}
        \clip (4.6,2) rectangle (7.6,11.5);
        \capbrace[sp]{(4.6,2)}{(4.6,13)}
      \end{scope}
      \draw node[right=0cm of sp] { sp };
    \end{tikzpicture}
  \caption{}
  \label{fig:illu-adv-data}
  \end{subfigure}
  \begin{subfigure}{0.333\linewidth}
    \begin{tikzpicture}[scale=.5, every node={scale=.5}]
    % recurrent parts
    \stdstackstart

@@

      % Stack pointer
      \begin{scope}
        \clip (4.6,2) rectangle (7.6,11.5);
        \capbrace[sp]{(4.6,2)}{(4.6,13)}
      \end{scope}
      \draw node[right=0cm of sp] { sp };
    \end{tikzpicture}
  \caption{}
  \label{fig:illu-clear-all}
  \end{subfigure}
  \caption{Illustration of the situations related to stack clearing when returning to an adversary.
    The greyed out areas are parts of the stack that are not accessible at the time. }
  \label{fig:ret-adv}
\end{figure}
\textbf{Invoking the adversary} A slightly more complex case is invoking the
adversary. As above, we clear all the non-argument registers, as well as the
part of the stack that we are not using (because, as above, it may contain local
capabilities from previously executed code that the adversary could exploit in
the same way). We leave a copy of the stack pointer in $r_\stk$, but only after
we have used the $\subseg{}{}{}$ instruction to shrink its authority to the part
that we are not using ourselves.
